### 2020-07-27 draft.Rmd
addressed some PR comments

We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial

@@

@@

$H_a$

To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (k * (k - 1))`$[@Higgins]

@@

seed_balchange = seed_accounts$balchange
marketing_balchange = (treated %>% filter(marketing==1))$balchange
control_balchange = (treated %>% filter(control==1, marketing==0))$balchange

>>>>

We will be testing the following hypothesis where $\theta_d$ is the median of the differences in savings for customers with SEED accounts from before and after the trial

@@

The Wilcoxon Signed-Rank Test requires three assumptions:

1. The data is paired and comes from the same population
2. Each pair is chosen randomly and independently
3. The data is continuous.

@@

$H_a: \exists i,j \text{ s.t. } \theta_i \leq\theta_j$ and $i,j\in \{x,y,z\}$

To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (3 * (3 - 1))`$[@Higgins]

@@

seed_balchange = seed_accounts$balchange
marketing_balchange = treated %>% 
  filter(marketing==1)%>%
  pull(balchange)
control_balchange = treated %>% 
  filter(control==1, marketing==0) %>%
  pull(balchange)
